\documentclass[12pt, a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{top=1in, bottom=1in, left=1.25in, right=1in}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{enumitem}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\setstretch{1.5}

\begin{document}

\begin{center}
    \textbf{\Large FORM 2} \\
    \textbf{THE PATENTS ACT, 1970 (39 of 1970)} \\
    \textbf{\&} \\
    \textbf{THE PATENTS RULES, 2003} \\
    \vspace{1cm}
    \textbf{\Large COMPLETE SPECIFICATION} \\
    [See section 10 and rule 13]
\end{center}

\vspace{1cm}

\noindent \textbf{1. TITLE OF THE INVENTION:} \\
\textbf{``A DECOUPLED MULTI-PROCESS ARCHITECTURE FOR ASYNCHRONOUS SPATIAL AND ACOUSTIC HUMAN-COMPUTER INTERACTION''}

\vspace{1cm}

\noindent \textbf{2. APPLICANT(S):} \\
(a) \textbf{Name:} Chirag Phogat, Chava Harshavardhan, Lalmalsawm Guite, Kaushal Pathak \\
(b) \textbf{Nationality:} Indian \\
(c) \textbf{Address:} Lovely Professional University, Phagwara, Punjab, India

\vspace{1cm}

\noindent \textbf{3. PREAMBLE TO THE DESCRIPTION:} \\
The following specification particularly describes the invention and the manner in which it is to be performed.

\newpage

\section*{FIELD OF THE INVENTION}
The present invention pertains to the field of software engineering, human-computer interaction (HCI), and native machine automation. In particular, it relates to the methodology and architecture of a multimodal operating system kernel that processes decoupled spatial geometries alongside localized natural language processing pipelines natively across isolated computing processors to execute zero-latency graphical actuations absent of external cloud communication.

\section*{BACKGROUND OF THE INVENTION AND PRIOR ART}
Modern human-computer workflows are severely tethered to mechanical peripheral devices, primarily keyboards and mice. Attempts to supersede these interfaces historically lean upon cloud-based Artificial Intelligence (AI) solutions relying exclusively on external servers to process natural speech. However, maintaining reliance on remote endpoint Application Programming Interfaces (APIs) mandates severe synchronous network latency, effectively rendering standard human graphical navigation (e.g., executing a cursor click or scrolling a web page) unacceptably slow.

Furthermore, integrating offline machine learning models over standard host-computing infrastructure invokes critical systemic blockages. In widely used dynamic languages, global interpreter locks mathematically forbid the parallel execution of concurrent bytecode. Therefore, when traditional configurations attempt to evaluate a moving human hand against a three-dimensional spatial matrix while simultaneously transcribing raw audio waveforms into linguistic text, the systems experience devastating memory collision, resulting in total visual frame pausing (cursor stalling) while the auditory node concludes generation.

Furthermore, classical computer-vision approaches deploy heavy Convolutional Neural Networks (CNN) merely to identify general classification patterns resulting in exorbitant CPU allocation and spatial depth discrepancies. The existing prior art entirely lacks a mechanism to natively buffer visual pixel matrices efficiently over isolated asynchronous pipelines, preventing accessible and reliable native interface modifications without network connectivity. 

\section*{OBJECTS OF THE INVENTION}
The primary object of the present invention is to provide a multi-process interaction architecture structured to negate synchronous system lock states, thereby permitting the simultaneous computation of optical matrices and NLP queries.

Another objective is to entirely supplant neural machine-learning image classifiers with a mathematical distance array methodology focusing strictly on the collision of bounding topological nodes, dramatically neutralizing environmental depth degradation.

Yet another objective is the orchestration of an offline Retrieval-Augmented Generation (RAG) base-64 bridge to empower local intelligence containers to analyze hardware screen buffers natively via isolated random access memory, bypassing disk read/write constraints.

\section*{SUMMARY OF THE INVENTION}
In a preferred embodiment, the invention manifests as a modular substructure decoupling the host operating system inputs into parallel isolated subsystems. By instantiating visual geometric processing over Processor Core 0 and auditory interpretation over Processor Core 1, mutual exclusion is enforced across computing memories. System communication is routed distinctly via a unified Inter-Process Communication (IPC) file buffer, drastically eliminating interpreter synchronization failures. 

To conduct spatial movements physically within the hardware screen dimensions, the invention abstracts human limb interaction into a strict Boolean intersection pattern based strictly upon Y-coordinate variations, whereby human actuation vectors undergo aggressive exponential mass averaging constants (e.g., $\alpha = 0.20$). To completely strip biological tendon twitching during fine actuations, the architecture implements a definitive ``Magnetic Cursor Lock'', which mathematically freezes all Cartesian translational updates the precise millisecond an index-to-thumb proximity boundary breaches a localized 60-pixel threshold. System hardware alterations like graphical brightness intensity execute natively over auxiliary daemon processors independent of the global loop space.

\section*{BRIEF DESCRIPTION OF THE ACCOMPANYING DRAWINGS}
\begin{itemize}
    \item \textbf{Fig 1:} Illustrates the architectural multi-process diagram establishing the separated IPC memory heaps.
    \item \textbf{Fig 2:} Diagrams the geometric collision zone mapping the exponential threshold bounding parameter between Index-Node 4 and Thumb-Node 8 interactions.
    \item \textbf{Fig 3:} Maps the execution pipeline representing the recursive Local Host NLP logic ingestion bypassing native OS threading.
\end{itemize}

\section*{DETAILED DESCRIPTION OF THE INVENTION}
The embodiments disclosed herein are descriptive of a high-performance native spatial interaction platform fundamentally devoid of requisite external cloud computation networks. In particular, the underlying execution logic explicitly intercepts peripheral input devices to establish a unified multimodal kernel. 

Firstly, to evade catastrophic execution collision, an initialization controller distributes the core logic processes across completely distinctly spawned local threads. The visual execution loop operates as the primary user-interface architecture, continuously interrogating the native CMOS optic array to capture uniform RGB matrices while the auditory loop acts strictly as a secondary fallback. To circumvent algorithmic CNN bloat, spatial interpretation implements finite mathematical bounding calculations. A Euclidean collision target dictates an expanded overlapping spatial dimension bounding up to $55$ contiguous pixels mathematically compensating for native hardware display scaling modifications and subject Z-axis distortions. For optical operations, structural X/Y tracking is natively de-coupled from inherently jittered irises and bound strictly to FaceMesh Node 1 (Nose Tip). By contrast, simple Boolean gating is supplanted by a rigorous Time-Gated Ocular matrix. By measuring isolated Eye Aspect Ratios (EAR) actively across sequential timestamps, the subsystem inherently dictates hardware macro variations natively: sub-$0.45$ second actuations fire primitive primary clicks, $0.45-2.0$ second holds invoke secondary interface clicks, and holds exceeding $2.0$ seconds forcefully trigger an OS logic override, deliberately shutting down the ocular processor to re-route memory allocation natively into spatial hand arrays entirely offline.

Concurrently, a discrete auditory thread captures phonemic arrays across a continuous recording threshold. Once activated via an atomic wake-pattern execution cycle, this separate thread serializes the transcription through a contained deterministic NLP reasoning network. 

The integration of local machine components transpires completely across the IPC file buffer state, removing synchronous software interruptions. Actions inherently invoking mechanical hardware lag, particularly graphical host alterations utilizing OS Management Instrumentation structures, are forcefully pushed onto detached sub-processing daemons. Further, advanced contextual reasoning requests from the end-user instantiates native buffer screenshots bypassing hard drive limitations, actively synthesizing a direct visual stream encoded by binary strings and pushed into the designated local optical intelligence endpoint via Port 11434 loops.

\newpage

\section*{CLAIMS}
\textbf{We claim:}

\begin{enumerate}[label=\arabic*.]
    \item A system for multimodal human-computer interaction capable of negating global interpreter execution latency, comprising:
    \begin{itemize}
        \item an initialization controller natively orchestrating independent subprocess execution strings isolated to unique host-processor memory heaps;
        \item an isolated optical engine determining physical spatial trajectory parameters independent of external neural classification APIs;
        \item a localized asynchronous sound wave interpretation pipeline bound to a persistent phoneme monitor constraint;
        \item a volatile inter-process communication bridge continuously cross-verifying Boolean status payloads spanning the severed processes without execution delays or blockages.
    \end{itemize}
    
    \item The system as claimed in claim 1, wherein the local optical engine eschews machine learning identification for quantitative geometric node collision methodology ensuring zero-latency mapping despite physical end-user focal shifting.
    
    \item The method as claimed in claim 2, wherein the mapping geometry implements a mathematical target overlap threshold equal to or greater than $55$ pixel boundaries, mechanically normalizing volumetric distance rendering discrepancies natively across disparate graphical magnifications.
    
    \item The method of interaction mapped in claim 1, wherein spatial coordinates generated by the optical interface are uniformly dampened through a dual-variable exponential moving average scalar equal definitively to $\alpha = 0.55$, functionally eradicating organic physical operator tremors prior to operating system cursor manipulation.
    
    \item The interaction framework described in Claim 1, in which deep internal hardware alterations, specifically brightness manipulation arrays, invoke isolated and disconnected subsystem daemon threads allowing synchronous polling termination without blocking the core native visual loop.
    
    \item The communication system as claimed in claim 1, integrating a retrieval-augmented generation parsing methodology capable of capturing and storing high-definition physical monitor displays strictly into active random access memory configurations sequentially avoiding mechanical drive input-output limitations.
    
\end{enumerate}

\newpage

\section*{ABSTRACT OF THE INVENTION}
A fully localized, decoupled multi-process Operating System framework capable of executing parallel native hardware automation via simultaneous spatial geometry matrices and localized acoustic phoneme routing. To structurally eliminate the visual frame pausing caused intrinsically by single-thread linguistic constraints, the platform mechanically distributes optical loop rendering and audio logic synthesis completely entirely into parallel CPU processes linked uniformly by a volatile Inter-Process Communication network. By integrating exact algorithmic bounding matrices, heavily weighted mathematical smoothing constraints, and explicit RAM-buffered Retrieval-Augmented Visual Generation architectures, the framework definitively usurps legacy peripheral control units allowing frictionless offline multimodal interface manipulations devoid of latency and cloud dependencies.

\vspace{2cm}

\noindent \textbf{Dated this [Insert Date] day of [Insert Month/Year].} \\
\vspace{1cm} \\
\noindent \textbf{Signature:} \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_ \\
\noindent (Chirag Phogat) \\
\noindent Lead System Architect / Applicant

\end{document}
